Deciding Bitvector Termination with Program Synthesis

### 2014-06-30 papers/termination/table.tex
Reran benchmarks

svcomp1 & 17 & unk & true & true & false & false & 1 & 5 & term & 9.6s\\

svcomp2 & 13 & unk & false & true & false & false & 1 & 5 & term & 10.2s\\

svcomp3 & 15 & unk & true & true & false & false & unk & 5 & unk & T/O\\

svcomp4 & 14 & unk & true & unk & true & false & unk & 5 & unk & T/O\\

svcomp7 & 9 & unk & true & true & true & false & 1 & 5 & unk & T/O\\

svcomp8 & 9 & unk & true & unk & false & false & unk & 5 & unk & T/O\\

svcomp9 & 12 & unk & true & unk & false & false & unk & 5 & term & 9.3s\\

svcomp10 & 15 & unk & true & true & false & false & 1 & 5 & term & 61.2s\\

svcomp11 & 16 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp17 & 17 & unk & true & true & false & false & 1 & 5 & nonterm & 19.0s\\

svcomp25 & 12 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp26 & 23 & unk & true & true & false & false & 1 & 5 & term & 38.7s\\

svcomp27 & 13 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp28 & 18 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp29 & 9 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp37 & 22 & unk & true & true & false & false & 1 & 5 & term & 12.3s\\

svcomp38 & 16 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp39 & 56 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp42 & 22 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

>>>>

loop1.c & 6 & unk & true & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop2.c & 7 & unk & true & true & false & false & 1 & 5 & term & 2.7s & 5\\

loop3.c & 8 & true & true & true & true & false & 1 & 5 & term & 3.4s & 8\\

loop4.c & 13 & unk & true & true & false & false & 2 & 5 & term & 3.9s & 13\\

loop5.c & 13 & unk & true & true & false & false & 2 & 5 & term & 7.9s & 25\\

loop6.c & 6 & unk & false & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop7.c & 7 & unk & true & unk & false & false & unk & 5 & unk & T/O & 0\\

loop8.c & 6 & unk & true & true & true & true & 1 & 5 & term & 2.7s & 1\\

loop9.c & 11 & true & true & false & false & false & 1 & 5 & term & 3.3s & 1\\

loop10.c & 6 & unk & true & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop43.c & 9 & unk & true & false & false & false & ? & 5 & term & 3.3s & 1\\

loop44.c & 9 & unk & true & false & false & false & ? & 5 & unk & T/O & 0\\

loop45.c & 15 & unk & true & false & false & false & ? & 5 & term & 7.9s & 23\\

loop46.c & 9 & unk & true & false & false & false & ? & 5 & term & 2.8s & 5\\

loop47.c & 6 & unk & true & false & false & false & ? & 5 & term & 3.0s & 1\\

loop48.c & 7 & unk & true & false & false & false & ? & 5 & term & 2.6s & 2\\

svcomp1.c & 17 & unk & true & true & false & false & 1 & 5 & term & 2.8s & 3\\

svcomp2.c & 13 & unk & false & true & false & false & 1 & 5 & term & 3.1s & 12\\

svcomp3.c & 15 & unk & true & true & false & false & unk & 5 & unk & T/O & 0\\

svcomp4.c & 14 & false & true & unk & true & false & unk & 5 & unk & T/O & 0\\

svcomp5.c & 18 & unk & true & false & true & false & unk & 5 & unk & T/O & 0\\

svcomp6.c & 11 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp7.c & 9 & unk & true & true & true & false & 1 & 5 & term & 19.0s & 18\\

svcomp8.c & 9 & unk & true & unk & false & false & unk & 5 & unk & T/O & 0\\

svcomp9.c & 12 & unk & true & unk & false & false & unk & 5 & term & 3.3s & 14\\

svcomp10.c & 15 & unk & true & true & false & false & 1 & 5 & term & 7.9s & 23\\

svcomp11.c & 16 & unk & true & true & false & false & 1 & 5 & term & 13.3s & 33\\

svcomp12.c & 13 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp13.c & 11 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp14.c & 18 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp15.c & 30 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp16.c & 17 & unk & true & true & false & false & 1 & 5 & term & 2.8s & 6\\

svcomp17.c & 17 & unk & true & true & false & false & 1 & 5 & nonterm & 9.5s & 3\\

svcomp18.c & 19 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp19.c & 21 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp20.c & 24 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp21.c & 22 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp22.c & 23 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp23.c & 22 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp24.c & 28 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp25.c & 12 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp26.c & 23 & unk & true & true & false & false & 1 & 5 & term & 5.7s & 16\\

svcomp27.c & 13 & false & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp28.c & 18 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp29.c & 9 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp30.c & 14 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp31.c & 7 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp32.c & 10 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp33.c & 18 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp34.c & 8 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp35.c & 7 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp36.c & 11 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp37.c & 22 & unk & true & true & false & false & 1 & 5 & term & 5.3s & 25\\

svcomp38.c & 16 & true & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp39.c & 56 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\

svcomp40.c & 12 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp41.c & 12 & unk & true & true & false & false & 1 & 5 & err & -- & 0\\

svcomp42.c & 22 & unk & true & true & false & false & 1 & 5 & unk & T/O & 0\\
